English-Chinese Translation Machine Based on Sequence to Sequence Network

### 2022-11-26 ML1/paper.tex
11-26

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is an important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} used convolutional neural network (CNN). This experience use method raised by \cite{8080244} to detection faces in photos.

@@

\section{Experiments}
\subsection{Dataset}
Training dataset includes more than ten thousand photos and all of them has at least one people facing to camera. Test dataset includes more than one thousand photos. In experience's testing procession, all images in test dataset were been marked by O-Net.

@@

\section{Conclusion}
	Multi-task convolutional neural network can play a crucial role in face detection. In this experience, we use three models to detect faces in photos. Due to lots parameter in models, it cost a long time to train all detection model in laptop. In training processing, we used late version pytorch to train models so python interpreter gave a warning in \textit{torch.nn}.

>>>>

% Each section begins with a \section{title} command
\section{Introduction}
	% \PARstart{}{} creates a tall first letter for this first paragraph
\PARstart{F}{ace} detection is an important research hotspot in computer vision research field. Nowadays, it plays a significant role in auto-driving and smart home IoT system. Some methods like \cite{ZHAN201619} and \cite{8080244} used convolutional neural network (CNN). This experience use method raised by \cite{7553523} to detection faces in photos.

@@

This model's loss in labels can be implemented directly with a sample type indicator. While the overall learning target can be formulated as equation.\ref{target1}.

\begin{equation}
    min\sum_{i=1}^{N}\sum_{j \in \left det,box,landmark \right }\alpha_{j} \beta_{i}^{j} L_{i}^{j}\label{target1}
\end{equation}

\section{Experiments}
\subsection{Dataset}
Training dataset includes more than ten thousand photos and all of them has at least one people facing to camera. Test dataset includes more than one thousand photos. In experience's testing procession, all images in test dataset were been marked by O-Net. Training process cost many time because this experience needs lots GPU processing power. In final, we uesd the parameter file provided with code to verify the model's responsibility in face detection.

@@

\section{Conclusion}
	Multi-task convolutional neural network can play a crucial role in face detection. In this experience, we use three models to detect faces in photos. Due to lots parameter in models, it cost a long time to train all detection model in laptop. In training processing, we used late version pytorch to train models so python interpreter gave a warning in \textit{torch.nn}. In this experience, we used a machine learning to handle a mission in face detection, it realized me that different networks in model has its responsibilities respectively, in which generating bounding boxes for P-Net, removing no-face bounding boxes for R-Net while add landmark in photos for O-Net.

### 2022-11-26 ML2/paper.tex
11-26

% Main Part
\section{Methods and Theory}

>>>>

% Main Part
\section{Methods and Theory}
In this experience, its algorithm elaborates an encoder-decoder model with attention mechanism and conditional possibility in machine translation. In this algorithm, it defined a sentence like $ Y=[y_1,y_2,...,y_{t}] $. In this case, conditional probability distribution $ p(Y) $ in sequence Y is equation.\ref{probability} while T is the length of whole sentence and $ c  $ is the semantic vector calculated from each hidden state form a sentence in equation.\ref{sv}.

\begin{equation}
    p(Y)= \prod_{t=1}^{T} \label{probability}p(y_t|y_1,y_2,...,y_{t},c)
\end{equation}

\begin{equation}
    c=q([h_1,h_2,...,h_T]) \label{sv}
\end{equation}

For attention mechanism this algorithm used contributes a hidden state in procession of machine learning for a neural cell to another like equation.\ref{hidden} while $ f(\cdot) $ is the function to calculate hidden state from $ x_t $ and $ h_{t-1} $.

\begin{equation}
    h_t=f(x_t,h_{t-1}) \label{hidden}
\end{equation}
